### 2015-11-07 CVPR16/Source/applications.tex
changes

Given 2D image points $\{\bu_j\}$ which are tracked between consecutive frames and a set of objects $\{O_i\}$ appearing in the frames, we aim to associate $\bu_j$ with $O_i$. Based on our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ between point track $\bu_j$ and object $O_i$ at depth $\lambda$ can be defined as
\begin{align}
\assocP = \Prefl\Ptrans,
\label{eq:defineassocP}
\end{align}
where $\Prefl$ and $\Ptrans$ are from \eqref{eq:evalPrefl} and \eqref{eq:evalCumulativePtrans} respectively. Note that the fraction $\assocP$ although called association probability does not capture the entire information that we have available for computing association of point tracks to objects.

To compute the association probability between point track $\bu_j$ and object $O_i$, we should also use the reprojection error. When the association of point track $\bu_j$ and object $O_i$ is correct and the point of reflection is at depth $\lambda$, the corresponding reprojection error $\Ereproj(\lambda)$ must be zero \eqref{eq:reprojerror}, otherwise the error becomes a measure of distance from the true solution. The error $\Ereproj(\lambda)$ can be used for associating point tracks and objects by converting it to the probability domain as
\begin{align}
  P^{ij}_{\text{reproj}}(\lambda) = \frac{1}{Z}\exp(-\Ereproj(\lambda)),
\label{eq:Passocbyreproj}
\end{align}
where $Z$ is the normalization coefficient.

@@

In contrast to the principled approach above, a heuristic baseline may simply assign a point track to the detection bounding box enclosing it (and background if outside all bounding boxes). For regions where bounding boxes overlap, it may assign point tracks to the object that has the smallest mean depth among the competing bounding boxes. As we will demonstrate in the experiments, such heuristics are sub-optimal compared to using \eqref{eq:prob-assoc} inspired by our occlusion model.

@@

We exploit in this section the application of our continuous occlusion model to 3D localization in road scenes, which further demonstrates the versatility of the proposed model. Given a set of tracked feature points $\{\bu_j(t)\}$ and 2D detection bounding boxes $\{\bb{i}\}$ at frame $t$, the goal is to localize 3D traffic participants (TPs), in particular, for each TP, estimating its position $\bp^i(t)$ and orientation $\bomega^i(t)$ on the ground plane and its 3D dimensions $\bB^i(t)$. We build a graphical model for representing object relationships and decompose the negative log likelihood as follows
%
\begin{multline*}
  -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i(t) \} | \{\bu_j(t)\} , \{\bb{i}\} )} = \\
  -Z 
   + \sum_{t=s_i}^{e_i} \lambda_t\EnergyTrack
  + 
  \sum_{t=s_i}^{e_i}
  \sum_{i=1}^N  
  %\sum_{\substack{i \in [1, \dots, N] \\t \in [s_i, \dots e_i]}}
  \lambda_d\EnergyBBox
  + \lambda_{\text{dyn}}\EnergyDyn
  + \lambda_{\text{size}}\EnergySize
  \enspace,
\end{multline*}
%
where $\pEnergy{track}$ and $\Energy{detect}$ reason about image observations such as point tracks and bounding boxes while $\Energy{dyn}$  and $\Energy{size}$ impose smoothness constraints and size priors respectively. Here, $\lambda_{track}$, $\lambda_{detect}$, $\lambda_{dyn}$, $\lambda_{size}$ are energy weights, $N$ is the number of objects in the sequence, $s_i$ and $t_i$ are respectively the starting and ending frames of object $O_i$, and $Z$ is the normalization coefficient. Figure~\ref{fig:graphmodel} illustrates an example of the graph and energies. Next, we present our unified continuous occlusion modelling for both point track and bounding box energies. Due to space constraints, we present the details of other energies in the supplementary.

@@

\subsubsection{Continuous point tracks energy with occlusion}
\label{sec:totalContPtTracksEnergy}

Let $\relp{i}{t}$ be the pose of object $O_i$ with respect to the camera at time $t$. We denote $\projectionOf{.}$ and $\invProjectionOftm{.}$ for the forward and inverse projection functions that project a 3D point to the camera image and vice versa. Then, the reprojection error for the 2D point $\trackp{t}$ with hypothesized depth $\lambda$, is given by
\begin{equation}
\Ereproj(\lambda) = \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2.
\label{eq:reprojerror}
\end{equation}
Note that inverse projection $\invProjectionOf{.}$ depends on both the 2D point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection is dependent on object pose at time $t-1$ while the forward projection depends on pose at time $t$, which can be different.

@@

\vspace{-0.3cm}
\paragraph{Inference on graphical model}
We apply Metropolis Hastings method~\cite{mackay1998introduction} for performing inference on the graphical model. Since we are optimizing over continuous variables, we use Gaussian distribution as the proposal function. We choose this over alternatives such as blocked coordinate descent since they are slower in our experiments.

>>>>

Given 2D image points $\{\bu_j\}$ which are tracked between consecutive frames and a set of objects $\{O_i\}$ appearing in the frames, we aim to associate $\bu_j$ with $O_i$. Based on our continuous occlusion model in Section~\ref{sec:setup}, the association probability $\assocP$ between point track $\bu_j$ and object $O_i$ at depth $\lambda$ can be defined as
\begin{align}
\assocP = \Prefl\Ptrans,
\label{eq:defineassocP}
\end{align}
where $\Prefl$ and $\Ptrans$ are from \eqref{eq:evalPrefl} and \eqref{eq:evalCumulativePtrans} respectively. Note that the fraction $\assocP$, although called association probability, does not capture the entire information that we have available for computing the association of point tracks to objects.

Rather, to compute the association probability between point track $\bu_j$ and object $O_i$, we should also use the reprojection error. When the association of point track $\bu_j$ and object $O_i$ is correct and the point of reflection is at depth $\lambda$, the corresponding reprojection error $\Ereproj(\lambda)$ must be zero \eqref{eq:reprojerror}, otherwise the error becomes a measure of distance from the true solution. The error $\Ereproj(\lambda)$ can be used for associating point tracks and objects by converting it to the probability domain as
\begin{align}
  P^{ij}_{\text{reproj}}(\lambda) = \frac{1}{Z}\exp(-\Ereproj(\lambda)),
\label{eq:Passocbyreproj}
\end{align}
where $Z$ is the normalization coefficient.

@@

In contrast to the principled approach above, a heuristic baseline may simply assign a point track to the detection bounding box enclosing it (and background if outside all bounding boxes). For regions where bounding boxes overlap, it may assign point tracks to the object that has the smallest mean depth among the competing bounding boxes. As we demonstrate in our experiments, such heuristics are sub-optimal compared to using \eqref{eq:prob-assoc} from our occlusion model.

@@

We exploit in this section the application of our continuous occlusion model to 3D localization in road scenes, which further demonstrates the versatility of the proposed model. Given a set of tracked feature points $\{\bu_j(t)\}$ and 2D detection bounding boxes $\{\bb{i}\}$ at frame $t$, the goal is to localize 3D traffic participants (TPs), in particular, for each TP, estimating its position $\bp^i(t)$ and orientation $\bomega^i(t)$ on the ground plane and its 3D dimensions $\bB^i(t)$. We build a graphical model for representing object relationships and decompose the negative log likelihood as follows
%
\begin{multline*}
  -\log{P(\{ \bp^i(t) , \bomega^i(t) , \bB^i(t) \} | \{\bu_j(t)\} , \{\bb{i}\} )} = \\
  -Z 
   + \sum_{t=s_i}^{e_i} \lambda_t\EnergyTrack
  + 
  \sum_{t=s_i}^{e_i}
  \sum_{i=1}^N  
  %\sum_{\substack{i \in [1, \dots, N] \\t \in [s_i, \dots e_i]}}
  \lambda_d\EnergyBBox
  + \lambda_{\text{dyn}}\EnergyDyn
  + \lambda_{\text{size}}\EnergySize
  \enspace,
\end{multline*}
%
where $\pEnergy{track}$ and $\Energy{detect}$ reason about image observations such as point tracks and bounding boxes while $\Energy{dyn}$  and $\Energy{size}$ impose smoothness constraints and size priors respectively. Here, $\lambda_{t}$, $\lambda_{d}$, $\lambda_{dyn}$, $\lambda_{size}$ are energy weights, $N$ is the number of objects in the sequence, $s_i$ and $t_i$ are respectively the starting and ending frames of object $O_i$ and $Z$ is the normalization coefficient. Figure~\ref{fig:graphmodel} illustrates an example of the graph and energies. Next, we present our unified continuous occlusion modelling for both point track and bounding box energies. Due to space constraints, we present the details of other energies in the supplementary material.

@@

\vspace{-0.3cm}
\paragraph{Continuous point tracks energy with occlusion}
%\label{sec:totalContPtTracksEnergy}
Let $\relp{i}{t}$ be the pose of object $O_i$ with respect to the camera at time $t$. We denote $\projectionOf{.}$ and $\invProjectionOftm{.}$ for the forward and inverse projection functions that project a 3D point to the camera image and vice versa. Then, the reprojection error for the 2D point $\trackp{t}$ with hypothesized depth $\lambda$, is given by
\begin{equation}
\Ereproj(\lambda) = \left\|\trackpj{t} - \projectionOf{\invProjectionOftm{\trackpj{t-1}, \lambda}}\right\|^2.
\label{eq:reprojerror}
\end{equation}
Note that inverse projection $\invProjectionOf{.}$ depends on both the 2D point $\trackp{t}$ and the unknown depth $\lambda$. Also note that the inverse projection is dependent on object pose at time $t-1$ while the forward projection depends on pose at time $t$, which can be different.

@@

\vspace{-0.3cm}
\paragraph{Inference on graphical model}
We apply Metropolis Hastings method~\cite{mackay1998introduction} for performing inference on the graphical model. Since we are optimizing over continuous variables, we use Gaussian distribution as the proposal function. We choose this over alternatives such as block coordinate descent since they are slower in our experiments.

### 2015-11-07 CVPR16/Source/related.tex
changes

\vspace{-0.3cm}
\paragraph{Occlusion handling in tracking}
Occlusions have also been handled in tracking-by-detection frameworks by considering occluder patterns in the image \cite{Kwak_etal_2012,Wu_Nevatia_2007}. A notable exception is the work of Milan et al.~\cite{Milan_etal_2014} that explicitly models occlusion in the continuous domain to determine a visibility for each object in multi-target tracking. However, the occlusion model in \cite{Milan_etal_2014} is essentially the overlap of image projections of a Gaussian representation of the object. Our occlusion modeling, on the other hand, is fully 3D, based on physical modeling of object-ray intersections and much more general in determining the probability of a point in space as belonging to an object. While our model can also be used to determine a visibility ratio similar to \cite{Milan_etal_2014}, it has far more general applications and can be quantitatively evaluated, as shown by our experiments on point track associations.

>>>>

\vspace{-0.3cm}
\paragraph{Occlusion handling in tracking}
Occlusions have also been handled in tracking-by-detection frameworks by considering occluder patterns in the image \cite{Kwak_etal_2012,Wu_Nevatia_2007}. A notable exception is the work of Milan et al.~\cite{Milan_etal_2014} that explicitly models occlusions in the continuous domain to determine a visibility ratio for each object in multi-target tracking. However, the occlusion model in \cite{Milan_etal_2014} is essentially the overlap of image projections of a Gaussian representation of the object. Our occlusion modeling, on the other hand, is fully 3D, based on physical modeling of object-ray intersections and much more general in determining the probability of a point in space as belonging to an object. While our model can also be used to determine a visibility ratio similar to \cite{Milan_etal_2014}, it has far more general applications and can be quantitatively evaluated, as shown by our experiments on point track associations.
